Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2020-11-20 mice_synthesizing/paper.Rmd
Fix typo.

This approach can be straightforwardly extended to a synthetic data framework. However, rather than imputing missing data, we overimpute actually observed data, that is, we replace observed values by multiple imputations. For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$). Following the notation of @reiter_raghunathan_multiple_2007, let $Z_j = 1$ if any of the values of unit $j$ are to be replaced by imputations, and $Z_j = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$. Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y}^{(l)} = (\textbf{Y}^{(l)}_{rep}, \textbf{Y}_{nrep})$. Note the superscript $^{(l)}$ indicating the $l$th synthetic data set. Now, instead of imputing $\textbf{Y}^{(l)}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, we impute $\textbf{Y}^{(l)}_{rep}$ from the posterior distribution of $(Y_{rep} | \textbf{Y}, \textbf{Z}, \theta)$. This process results in $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $m$ the number of synthetic datasets.

By default, `mice` imputes all values that are coded as missing in the dataset. Using the `where` parameter within the mice function, one can choose to impute any value in the dataset. As input, the `where` parameter requires a matrix of the same dimensions of the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logical values.
<!--

>>>>

This approach can be straightforwardly extended to a synthetic data framework. However, rather than imputing missing data, we overimpute actually observed data, that is, we replace observed values by multiple imputations. For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$). Following the notation of @reiter_raghunathan_multiple_2007, let $Z_j = 1$ if any of the values of unit $j$ are to be replaced by imputations, and $Z_j = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$. Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y}^{(l)} = (\textbf{Y}^{(l)}_{rep}, \textbf{Y}_{nrep})$. Note the superscript $^{(l)}$ indicating the $l$th synthetic data set. Now, instead of imputing $\textbf{Y}^{(l)}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, we impute $\textbf{Y}^{(l)}_{rep}$ from the posterior distribution of $(Y_{rep} | \textbf{Y}, \textbf{Z}, \theta)$. This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $m$ the number of synthetic datasets.

By default, `mice` imputes all values that are coded as missing in the dataset. Using the `where` parameter within the mice function, one can choose to impute any value in the dataset. As input, the `where` parameter requires a matrix of the same dimensions of the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logical values.
